How unprecedented was the February 2021 Texas cold snap?

### 2021-05-06 doc/submission_02.tex
after creating new release, update link to zenodo DOI in paper

We are committed to open science.
Our open source code is freely available in a live repository at \url{https://github.com/jdossgollin/2021-TXtreme} and in an archived repository at \url{https://dx.doi.org/10.5281/zenodo.4568923}.

>>>>

We are committed to open science.
Our open source code is freely available in a live repository at \url{https://github.com/jdossgollin/2021-TXtreme} and in an archived repository at \url{https://dx.doi.org/10.5281/zenodo.4739881}.
